NumPy---Array Programming in Python

### 2020-01-27 body.tex
Small fix

NumPy combines the expressive power of \emph{array programming}, 
the performance of C, and the Python programming language in a mature,
well-tested, well-documented, and community developed library.
It builds on decades of work refining the array programming
syntax from APL through Yorick and others.
It also made it easy for other libraries to develop fast and
memory-efficient compiled code, usually in C or Fortran, that could manipulate
these arrays and pass them back to Python.
Popular array-aware libraries increased the user community and that
in turn led to more libraries adding new functionality
to the scientific Python ecosystem.

>>>>

NumPy combines the expressive power of \emph{array programming}, 
the performance of C, and
the readability, usability, and versatility of Python in a mature,
well-tested, well-documented, and community developed library.
It builds on decades of work refining the array programming
syntax from APL through Yorick and others.
It also made it easy for other libraries to develop fast and
memory-efficient compiled code, usually in C or Fortran, that could manipulate
these arrays and pass them back to Python.
Popular array-aware libraries increased the user community and that
in turn led to more libraries adding new functionality
to the scientific Python ecosystem.
